### 2015-06-25 provaVisao2015Casa.tex
Changed the sour to algorithm in q1-2

\documentclass[12pt]{article}
\usepackage[latin1,utf8]{inputenc}
\usepackage[brazil]{babel}
\usepackage{setspace}
\usepackage{boxedminipage}
\usepackage{latexsym}
\usepackage{multirow}
\usepackage[pdftex]{graphicx}
\usepackage{float}
\usepackage{url}
\usepackage{xcolor,listings}
\usepackage{amsmath,mathrsfs}
\usepackage{biblatex}
\addbibresource{references.bib}

@@

			Abaixo o trecho onde o algoritmo efetivamente foi implementado. O código completo está em \textbf{source/ela.py}.

			\begin{lstlisting}[basicstyle=\ttfamily]
			import os
			from PIL import Image, ImageChops, ImageEnhance
			from time import gmtime, strftime

			# you can change the image directory here
			HOAX_IMAGES = './HoaxImages/'

			def check_image(img_path, scale=20.0, show=False):
			""" Compute the Error Level Analysis for the given image

			Save a copy of the given image changing its quality level,
			in our case 95%, and compute the difference between this 
			image over the original. In addition, a scale is also 
			applied to the final result for better viewing.

			References: 
			http://blackhat.com/presentations/bh-dc-08/Krawetz/Whitepaper/bh-dc-08-krawetz-WP.pdf
			http://www.eecs.berkeley.edu/Pubs/TechRpts/2015/EECS-2015-85.pdf
			"""
			try:
			img = Image.open(img_path)
			except FileNotFoundError:
			print ("File '"+ img_path +"' not found.")
			return

			# check the image format for JPEG only
			if img.format is not 'JPEG':
			log(img_path + ' is not a JPEG file')
			return

			log("Image size "+ str(img.size[0]) + "x" + str(img.size[1]))
			short_file_name = os.path.splitext(img_path)[0]

			# save a copy of the image with a different inferior quality level
			resaved_path = short_file_name + '_resaved'
			img.save(resaved_path, 'JPEG', quality=95)
			resaved_img = Image.open(resaved_path)

			# compute the difference between the given image and the image
			# generated applying a scale to increase the brightness
			ela_img = ImageChops.difference(img, resaved_img)
			ela_img = ImageEnhance.Brightness(ela_img).enhance(scale)
			ela_img.save(short_file_name + '_ela.png')
			if (show):
			ela_img.show()

			os.remove(resaved_path)
			\end{lstlisting}

>>>>

\documentclass[12pt]{article}
\usepackage[latin1,utf8]{inputenc}
\usepackage[brazil]{babel}
\usepackage{setspace}
\usepackage{boxedminipage}
\usepackage{latexsym}
\usepackage{multirow}
\usepackage[pdftex]{graphicx}
\usepackage{float}
\usepackage{url}
\usepackage{xcolor,listings}
\usepackage{amsmath,mathrsfs}
\usepackage{biblatex}
\usepackage[portuguese, ruled, linesnumbered]{algorithm2e}
\addbibresource{references.bib}

@@

Abaixo o algoritmo que foi implementado onde utilizei o pacote pillow para as operações na imagem.
O código completo está em \textbf{source/ela.py}.

%Código
\begin{algorithm}[H]
    \SetKwData{Img}{ImagemOriginal}
    \SetKwData{ResavedImg}{ImagemComprimida}
    \SetKwData{ElaImg}{ImagemELA}
    \SetKwData{ImgPath}{Caminho\quad da\quad imagem}
    \SetKwData{ResavedPath}{Caminho\quad da\quad imagem comprimida}
    \SetKwFunction{abrirImagem}{abrirImagem}
    \SetKwFunction{salvarImagem}{salvarImagem}

    \SetAlgoLined
    \Entrada{Caminho\quad da\quad imagem, escala}
    \Saida{Imagem com ELA calculado}
    \BlankLine
    \Img $\leftarrow$ \abrirImagem{\ImgPath}\\
    \Se{\Img não é JPEG}{\Retorna{Nulo}}
    \BlankLine
    \salvarImagem{\ResavedPath, JPEG, qualidade}\\
    \ResavedImg $\leftarrow$ \abrirImagem{\ResavedPath}\\
    \BlankLine
    \Para{$x\leftarrow 0$ \Ate $largura\quad \Img$}{
        \Para{$y\leftarrow 0$ \Ate $altura\quad \Img$}{
            $pixel\_img\_original = \Img[x,y]$\\
            $pixel\_img\_comprimida = \ResavedImg[x,y]$\\
            $R = abs(pixel\_img\_original[0] - pixel\_img\_comprimida[0]) * escala$\\
            $G = abs(pixel\_img\_original[1] - pixel\_img\_comprimida[1]) * escala$\\
            $B = abs(pixel\_img\_original[2] - pixel\_img\_comprimida[2]) * escala$\\
            $\ElaImg[x,y] = [R, G, B]$
        }
    }
    \BlankLine
    \Retorna{\ElaImg}
    \label{alg1}
    \caption{\textsc{Error Level Analysis}}
\end{algorithm}
